%-------------------------
% Resume in Latex
% Author : Hung Ho
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Hung Ngoc Ho} \\ \vspace{1pt}
    \small  \href{mailto:ho.ngoc.hung2812@gmail.com}{\underline{ho.ngoc.hung2812@gmail.com}} $|$ (+358) 504488109  $|$
    \href{https://linkedin.com/in/hongochung}{\underline{linkedin.com/in/hongochung}} $|$
    \href{https://github.com/bpc1985}{\underline{github.com/bpc1985}}
\end{center}

%-----------PROFILE-----------
\section{Professional Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Highly motivated and experienced web developer with a focus on designing and implementing user-centric, high-performance websites. Strong commitment to web standards and a passion for emerging technologies, specializing in frameworks like ReactJS, NextJS, AWS and AI. Adept in both front-end and back-end development, consistently delivering scalable, reliable applications. Proven ability to thrive in agile environments, collaborating effectively with cross-functional teams to drive continuous integration and delivery.} \\
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Aalto University  }{Espoo, Finland}
      {Master's Degree in Engineering, Information Networks }{Sep. 2017 -- No Award}
    \resumeSubheading
      {Åbo Akademi University }{Turku, Finland}
      {Master's Degree in Engineering, Software Engineering }{Sep. 2015 -- May 2018}
    \resumeSubheading
      {Metropolia University of Applied Sciences }{Espoo, Finland}
      {Bachelor's Degree in Engineering, Media Engineering }{Sep. 2009 -- May 2014}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior Web Developer}{Sep 2021 -- Aug 2024}
      {ResultElf Oy}{Espoo, Finland}
      \resumeItemListStart
        \resumeItem{Developed a REST API using FastAPI and PostgreSQL as part of an internal project.}
        \resumeItem{Led the development of a full-stack web application for the Cresso platform using NodeJS, PostgreSQL, ReactJS, Typescript, Zustand, React-Query, MUI, Echarts, Docker and Kubernetes.}
        \resumeItem{Built a modern, responsive user interface using Next.js and TailwindCSS for the company website.}
        \resumeItem{Established unit testing, code coverage, CI/CD pipelines for frontend projects using Github Actions.}
        \resumeItem{Monitored and visualized frontend metrics with Amazon CloudWatch RUM.}
        \resumeItem{Integrated the Matomo web analytics platform for tracking online visits and generating analysis reports.}
        \resumeItem{Created Grafana queries to visualize data in dashboards.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Web Developer}{Jan 2020 -- Jul 2021}
      {Quanturi Oy}{Espoo, Finland}
      \resumeItemListStart
        \resumeItem{Developed a REST API using NodeJS, ExpressJS, MongoDB and RabbitMQ for the Quanturi monitoring dashboard's backend.}
        \resumeItem{Migrated outdated code to modern frontend web app with responsive interface using ReactJS, Redux, and MUI.}
        \resumeItem{Set up CICD pipelines for the dashboard project using AWS CodePipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {Web Developer}{Jul 2014 -- Oct 2019}
      {Verto Analytics Oy}{Espoo, Finland}
      \resumeItemListStart
        \resumeItem{Developed and maintained Verto's frontend applications using AngularJS, ReactJS, Redux, and Highcharts.}
        \resumeItem{Ensured the technical feasibility of UI/UX designs and optimized applications for performance and scalability.}
        \resumeItem{Managed CI pipelines with Jenkins and ensured compliance with required testing standards.}
        \resumeItem{Collaborated with users to gather feedback and implement improvements.}
        \resumeItem{Authored functional requirement documents and technical guides.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, \texttt{C\#}, Python, HTML/CSS, Javascript (ES6), Typescript} \\
     \textbf{Frontend}{: VueJS, ReactJS, NextJS, Redux, Zustand, Vite (Rollup), Micro-frontends, MUI, TailwindCSS} \\
     \textbf{Testing}{: Jasmine, Jest, Vitest, React Testing Library, Cypress, Code coverage with C8 } \\
     \textbf{Backend}{: Node.js, Express, FastAPI, Spring Boot, AWS Lambda} \\
     \textbf{Databases}{: MySQL, PostgreSQL, MongoDB, Prisma, GraphQL, AWS RDS, DynamoDB} \\
     \textbf{Mobile}{: React Native (Expo), Flutter (Basic)} \\
     \textbf{Tools}{: Git, Docker, Github Actions, AWS, VS Code, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Chart Libraries}{: Highcharts, Recharts, Echarts}
    }}
 \end{itemize}

\end{document}
